D-Hammer: Efficient Equational Reasoning for Labelled Dirac Notation

### 2025-04-07 05tool_eval.tex
.

\section{Implementation and Case Study}
We present \textbf{D-Hammer}, an open-source and publicly
available\footnote{{\textcolor{red}{URL}}} implementaion of our
approach.  \textbf{D-Hammer} is an equational prover for Labelled
Dirac notation written in \CC.  It features a parser built using
ANTLR4, and scalar reasoning is powered by the Mathematica
Engine. Users can use commands to make definitions and assumptions in
the maintained context, conduct the normalization and equivalence
checking, and obtain the rewriting trace output.  D-Hammer can be run
interactively from the command line or integrated into other
\CC\ projects as a library.

@@

\section{Evaluation}
We evaluate D-Hammer on several example sets, and make a comparison with the previous tool DiracDec~\cite{diracdec}.
The experiments are carried out using a MacBook Pro with M3 Max chip. Results are summarized as follows.

@@

The results show significant performance improvements. The enhanced
efficiency primarily results from algorithmic improvements rather than
the shift to a C++ implementation. This is supported by the fact that
efficiency gains are more significant for larger examples, as can be
observed in \Cref{fig: CoqQ plot}.

@@

>>>>

\section{Implementation and Case Study}
We present \textbf{D-Hammer}, an open-source and publicly
available\footnote{https://github.com/LucianoXu/D-Hammer} implementaion of our
approach.  \textbf{D-Hammer} is an equational prover for Labelled
Dirac notation written in \CC.  It features a parser built using
ANTLR4, and scalar reasoning is powered by the Mathematica
Engine. Users can use commands to make definitions and assumptions in
the maintained context, conduct the normalization and equivalence
checking, and obtain the rewriting trace output.  D-Hammer can be run
interactively from the command line or integrated into other
\CC\ projects as a library.

@@

\section{Evaluation}\label{sec:eval}
We evaluate D-Hammer on several example sets, and make a comparison with the previous tool DiracDec~\cite{diracdec}.
The experiments are carried out using a MacBook Pro with M3 Max chip. Results are summarized as follows.

@@

The results show significant performance improvements. The enhanced
efficiency primarily results from algorithmic improvements rather than
the shift to a \CC implementation. This is supported by the fact that
efficiency gains are more significant for larger examples, as can be
observed in \Cref{fig: CoqQ plot}.

@@

\subsubsection*{Equivalence checking of circuits}
\gb{TODO}
